\tool: Revisiting BadUSB with Type-C

### 2021-01-26 WOOT/BadUSBC.tex
Add implementation part and LaTeX writing convention
XD
add new convention about label, combine member's .tex,
fix reference
add util.tex
add outline
Comments
add impl part, todo: three mode
Balanced layout of references
complete the coutermeasure
Add page number
a pass on intro.
Anonymous

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Is It Possible to Steal Money Through USB-C?
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle
\thispagestyle{plain}

\begin{abstract}
Abstract~\cite{CGF1}.
\end{abstract}

\begin{IEEEkeywords}
BadUSB
\end{IEEEkeywords}

\input{./Files/introduction.tex}
\input{./Files/background.tex}
\input{./Files/related_work.tex}
\input{./Files/badusb.tex}
\input{./Files/experiment.tex}
\input{./Files/discussion.tex}
\input{./Files/conclusion.tex}
%\input{./Files/acknowledgement.tex}

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

\makeatletter
\def\lst@makecaption{%
  \def\@captype{table}%
  \@makecaption
}
\makeatother

\input{./Files/util.tex}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{\tool: Revisiting BadUSB with Type-C}

\author{Anonymous Authors}
%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
\outline{Brief intro of USB protocol}\\
\outline{Brief intro of Rubber Ducky}\\
\outline{What have we done, our contribution}\\
\outline{Our experiment/case study, Attack of shops}\\
\end{abstract}

\begin{IEEEkeywords}
USB;BadUSB
\end{IEEEkeywords}

\input{./Files/introduction.tex}
\input{./Files/background.tex}
\input{./Files/related_work.tex}
\input{./Files/badusb.tex}
\input{./Files/experiment.tex}
\input{./Files/countermeasure.tex}
\input{./Files/discussion.tex}
\input{./Files/conclusion.tex}
%\input{./Files/acknowledgement.tex}

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}
\balance
